\textbf{Personal Questions}
\begin{enumerate}
\item How many years have you spent in the fire engineering trade?
\item What is your relation to the fire engineering trade?
\end{enumerate}

\textbf{Design Phase}
\begin{enumerate}
\item Do you spend time risk assessing the property?
\item If you do a risk assessment, how do you carry out or identify the hazards?
\item At what stage are you normally brought onto the project?
\item When is a more suitable time to be brought onto the project?
\item Do you believe that not being brought onto a project early can affect the costs of the final project?
\item Do your designs only focus on life safety?
\item Are the majority of your designs mainly code compliant with a few ``trade offs'' for non code compliant areas?
\item Do you build in any form of redundancy into your designs?
\item Would you say your designs are inherently safe?
\end{enumerate}

\textbf{Costs}
\begin{enumerate}
\item In your design decisions, is cost the critical design factor?
\item Do you consider the costs of protection measures you specify?
\end{enumerate}

\textbf{Fire Protection}
\begin{enumerate}
\item Do you have to validate/verify your non code compliant designs?
\item Is there any guidance on what should be validated or verified?
\item How do you prove that a design you are proposing is equivalent to that specified in the codes?
\item How does the approvals process work?
\item Do you believe that Building Control reject your plans due to a lack of understanding in Fire Engineering?
\item Buildings are relying more on good design and less on active systems for ventilation and the like. Can you see fire engineering following this trend?
\item Do you specify extra passive fire protection rather than that just described in the codes?
\item If a certain protection method lowered costs for insurance for a building, would you specifiy that protection measure?
\item On a scale of 1-5, how essential do you think passive fire protection is?
\item On a scale of 1-5, how effective do you think passive fire protection is?
\end{enumerate}

\textbf{BS 9999}
\begin{enumerate}
\item How often do you use BS 9999 over other current codes?
\item Has BS 9999 changed your methods of design work?
\item Part of BS 9999 focuses on building management and the management of the building after completion. Do you provide the management plans?
\item Do you believe that BS 9999 reduces the scope for fire engineering?
\item Do you believe that BS 9999 offers a more cost effective method of design?
\item Does a design using BS 9999 take less time to complete a design, on average, than with previous design codes?
\item How have other project stakeholders taken to BS9999?
\item Do you believe that BS 9999 will help building owners comply with The Regulatory Reform Order?
\item Do you believe that the addition of sprinklers to reduce a risk profile is cost effective?
\item Do you still design non code compliant areas within buildings?
\item Do you think BS 9999 will have a positive effect on the management of the building's passive fire protection measures?
\item Considering the building is tailored to a specific risk profile, how severe can you see a change of risk profile being in the future?
\end{enumerate}
